Portal Forecast

### 2018-02-15 index.Rmd

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Contols', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Contols', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions,
            title=paste0(sp_predictions$forecast_date[2], ": Control plots"))

plot(sp_predict)
```
